Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-09 paper.tex
Add files via upload

As we have seen before, the resulting radio-emitting CRe distribution
depends on compressible turbulence (which sets the level of
reacceleration) and the distribution of pre-existing CRs. Hence we
vary parameters describing the amount of energy contained in
turbulence relative to the thermal energy, $X_{\rm tu}$, the spatial
profile of turbulence as parametrized by $\alpha_{\rm tu}$, as well as
the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
  spat}$ (see below).  In order to quickly explore this parameter
space, we solve the Fokker-Planck equation in static spherical shells
for injection, reacceleration, and losses of the CRs, i.e., we neglect
the Lagrangian trajectories during the re-acceleration time.  Once the
CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
calculate the resulting radio emission and compare the emission
profiles and spectra as we vary one parameter at the time relative to
our fiducial model.

@@

\subsection{Gamma rays}
The gamma-ray emission from CRps that produce decaying neutral pions
could be substantial if the CRps are reaccelerated efficiently enough,
hence it is interesting to estimate this emission for our models and
compare to upper limits. We predict the gamma-ray emission from
\Mflatturb (\Mstream) with $F_\gamma(>500\,\rmn{MeV})=4\times10^{-10}
(5\times10^{-10}) \mathrm{ \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes
from these models are slightly larger than in \cite{brunetti12}, where
the differences comes from our steeper CRp profiles in addition to
simulation based formalism we rely on that accounts for both Coulomb
and hadronic losses during the build up of the CR distribution in
contrast to the scaling relations adopted in their
paper. Interestingly the gamma-ray flux from both our scenarios are
just below recent Fermi-LAT limits derived from a gamma-ray profile
similar to \Mflatturb where
$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
  communication. See also
  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
  in the next few years by Fermi-LAT. } The spectral index of the CRp
distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
radio-emitting secondary CRes. The steep spectrum is ultimately a
consequence of the shock history of the simulated cluster, with a weak
dependence on our test particle model for Fermi-I acceleration
\citep{pinzke13}, where we steepen the spectral index to avoid
acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.

>>>>

As we have seen before, the resulting radio-emitting CRe distribution
depends on compressible turbulence (which sets the level of
reacceleration) and the distribution of pre-existing CRs. Hence we
vary parameters describing the amount of energy contained in
turbulence relative to the thermal energy, $X_{\rm tu}$, the spatial
profile of turbulence as parametrized by $\alpha_{\rm tu}$, as well as
the spatial CR profile that we will parametrize by $\alpha_{\rm CR,
  spat}$ (see below).  In order to quickly explore this parameter
space, we solve the Fokker-Planck equation in static spherical shells
for injection, reacceleration, and losses of the CRs, i.e., we neglect
the Lagrangian trajectories during the re-acceleration time.  Once the
CRs have been reaccelerated for $\tau_\rmn{cl} = 650\,\rmn{Myr}$, we
calculate the resulting radio emission \AP{numerically using the
  formalism outlined in \cite{1979rpa..book.....R}} and compare the
emission profiles and spectra as we vary one parameter at the time
relative to our fiducial model.

@@

\subsection{Gamma rays}
The gamma-ray emission from CRps that produce decaying neutral pions
could be substantial if the CRps are reaccelerated efficiently enough,
hence it is interesting to estimate this emission for our models and
compare to upper limits. \AP{We follow the formalism outlined in
  \cite{1999APh....12..169B} (and references therein) and calculate
  the gamma-ray emission numerically for our three models.} We predict
the gamma-ray emission from \Mflatturb (\Mstream) with
$F_\gamma(>500\,\rmn{MeV})=4\times10^{-10} (5\times10^{-10}) \mathrm{
  \,ph\, s}^{-1}\mathrm{cm}^{-2}$. The fluxes from these models are
slightly larger than in \cite{brunetti12}, where the differences comes
from our steeper CRp profiles in addition to simulation based
formalism we rely on that accounts for both Coulomb and hadronic
losses during the build up of the CR distribution in contrast to the
scaling relations adopted in their paper. Interestingly the gamma-ray
flux from both our scenarios are just below recent Fermi-LAT limits
derived from a gamma-ray profile similar to \Mflatturb where
$F_\gamma(>500\,\rmn{MeV})<5.3\times10^{-10} \mathrm{ \,ph\,
  s}^{-1}\mathrm{cm}^{-2}$ \footnote{Fabio Zandanel, private
  communication. See also
  \citet{2014MNRAS.440..663Z,2014ApJ...787...18A}. and will be probed
  in the next few years by Fermi-LAT. } The spectral index of the CRp
distribution is relatively steep ($\alpha_{\rmn{p}}\sim2.6$) for the
CRp energies $E \gtrsim 10$~GeV that are relevant for the injection of
radio-emitting secondary CRes. The steep spectrum is ultimately a
consequence of the shock history of the simulated cluster, with a weak
dependence on our test particle model for Fermi-I acceleration
\citep{pinzke13}, where we steepen the spectral index to avoid
acceleration efficiencies above $\zeta_{\rmn{p}} \sim 10\%$.
